---
title: "p8105_hw6_kh3074"
author: "KaiYu He(kh3074)"
date: "11/29/2021"
output: github_document
---

# Loading packages
```{r}
library(tidyverse)
library(modelr)
```


# Problem 1

### Data Cleaning
```{r}
baby_df = read_csv("data/birthweight.csv")
# Firstly check missing values.
colnames(baby_df)[colSums(is.na(baby_df)) > 0]
# There are no missing values in the dataframe

# Secondly change the class variables into factor
baby_df = 
  baby_df%>%
  mutate(babysex = as.factor(case_when(
    babysex == 2 ~ "female",
    babysex == 1 ~ "male"
  )))%>% 
  mutate(frace = as.factor(case_when(
    frace == 1 ~ "White",
    frace == 2 ~ "Black",
    frace == 3 ~ "Asian",
    frace == 4 ~ "Puerto Rican",
    frace == 8 ~ "Other"
  )))%>%
  mutate(mrace = as.factor(case_when(
    mrace == 1 ~ "White",
    mrace == 2 ~ "Black",
    mrace == 3 ~ "Asian",
    mrace == 4 ~ "Puerto Rican",
    mrace == 8 ~ "Other"
  )))%>%
  mutate (malform = as.factor(case_when(
    malform == 0 ~ "absent",
    malform == 1 ~ "present"
  )))
baby_df
baby_df%>%
  head(5)%>%
  knitr::kable()
```

- In the Data Cleaning I checked for the missing value and mutate all the class variable form double into factors.

### Propose a regression model for birthweight.
```{r}
#I think gestational and mother’s weight gain during pregnancy (pounds) are the key factors of babies' weight
my_fit = lm(bwt ~ gaweeks*wtgain ,data = baby_df)
my_fit %>%
  broom::tidy() %>%
  select(term, estimate, p.value) %>%
  knitr::kable(digits = 4)
#plot the residuals against the fitted values
baby_df%>%
  add_predictions(my_fit)%>%
  add_residuals(my_fit)%>%
  ggplot(aes(x = pred ,y = resid))+
  geom_violin()+
  labs(title = "Residules Vs prediction")
```
- I firstly draw plots about factors i'm interested in against the  to see 

- Comparison in terms of the cross-validated prediction error
```{r}
baby_cv_df = 
  crossv_mc(baby_df,100)%>%
  mutate(
    my_fit = map(train, ~lm(bwt ~ gaweeks*wtgain, data = .x)),
    fit1   = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    fit2   = map(train, ~lm(bwt ~ bhead * blength * babysex, data = as_tibble(.x)))) %>% 
  mutate(
    rmse_my_fit = map2_dbl(my_fit, test, ~rmse(model = .x, data = .y)),
    rmse_fit1   = map2_dbl(fit1, test, ~rmse(model = .x, data = .y)),
    rmse_fit2   = map2_dbl(fit2, test, ~rmse(model = .x, data = .y)))

#Now Drawing plots to compare
baby_cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()+
  labs(title="comparesion of three models")
```
- Apparently my modle doesn't goes well, the best model is the third one with head circumference, length, sex, and all interactions.  

# Problem 2

### Load Data
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

### boostrapping

- Checking rsquare  
```{r}
# r.squared
set.seed(1234)
r_squared_df = 
  weather_df %>%
  bootstrap(n = 5000) %>% 
  mutate(models = map(strap,~lm(tmax ~ tmin,data = .x)),
         results = map(models,broom::tidy),
         r2 = map(models,broom::glance))%>%
  select(-strap,-models)%>%
  unnest(r2)

r_squared_df

r_squared_df%>%
  ggplot(aes(x = r.squared))+
  geom_density()
```
- The distribution of r.squared is a bell shaped distribution with mean: `r mean(pull(r_squared_df,r.squared))`, and the standard deviation `r sd(pull(r_squared_df,r.squared))`, the 95% CI is [`r quantile((pull(r_squared_df,r.squared)),0.025)`,`r quantile((pull(r_squared_df,r.squared)),0.975)`]  

- Checking logbeta
```{r}
set.seed(1234)
logbeta_df = 
  weather_df %>%
  bootstrap(n = 5000) %>% 
  mutate(models = map(strap,~lm(tmax ~ tmin,data = .x)),
         results = map(models,broom::tidy))%>%
  select(-strap,-models)%>%
  unnest(results)%>%
  select(.id,term,estimate)%>%
  pivot_wider(names_from = term,values_from = estimate)%>%
  janitor::clean_names()%>%
  mutate(logbeta = log(intercept*tmin))

# Draw distribution of log(beta0 * beta1)
logbeta_df %>%
  ggplot(aes(x = logbeta))+
  geom_density()
```

- The distribution of $log(\beta_0 * \beta_1)$ is a bell shaped distribution with mean: `r mean(pull(logbeta_df,logbeta))`, and the standard deviation `r sd(pull(logbeta_df,logbeta))`, the 95% CI is [`r quantile((pull(logbeta_df,logbeta)),0.025)`,`r quantile((pull(logbeta_df,logbeta)),0.975)`]  







